Reproducible Results in Parsing-Based Machine Translation:\\ The JHU Shared Task Submission

### 2010-04-23 papers/wmt10.pipeline/paper.tex
Tidying up
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1602 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\author{Lane Schwartz\
\thanks{\ Research conducted as a visiting researcher at Johns Hopkins University}\
\\University of Minnesota\\Minneapolis, MN\\
{\tt lane@cs.umn.edu} \And
Chris Callison-Burch \\
Johns Hopkins University \\
Baltimore, MD\\
{\tt ccb@cs.jhu.edu}}

@@

\begin{abstract}
We present the JHU submission to the 2010 WMT shared translation task. We describe processing steps using open data and open source software used in our submission, and provide the scripts and configurations required to train, tune, and test the machine translation system described herein.
\end{abstract}

@@

Research investigating natural language process and computational linguistics can and should have an extremely low barrier to entry. The data with which we work is customarily available in common electronic formats. The computational techniques which we apply can typically be performed on commodity computing resources which are widely available. In short, there should be no reason why small research groups and even lone researchers should not be able to join and make substantive contributions furthering our field.
%
The reality is less encouraging.

@@

Freely available parallel corpora for numerous European languages have also been released in recent years. These include the Europarl \cite{Koehn-europarl} and JRC-Acquis \cite{Steinberger-2006} legislative corpora, each of which includes data for most EU language pairs. The smaller News Commentary \cite{Callison-Burch2007a,Callison-Burch2008a} provide smaller amounts of parallel data in the news genre. The recent Fr-En $10^9$ \cite{WMT09-Findings} corpus aggregates huge numbers of parallel French-English sentences from the web.

@@

Figure \ref{dependencyGraph} shows a graph depicting the steps in our experimental workflow, and the dependencies between steps. Each node in the graph represents a step in the workflow; each step is with a Make script that defines how to run the tools required in that step. In each experiment, an additional configuration script is provided for each experimental step, defining the parameters to be used when running that step in the current experiment. Optional front-end wrapper scripts can also be provided, allowing for a complete experiment to be run - from downloading data and software through truecasing translated results - by executing a single make file.

@@

Following \newcite{Joshua-WMT}, a subset of the available training sentences is selected via subsampling; training sentences are selected based on the estimated likelihood of that sentence being useful later for translating a particular test corpus.

@@

Because of the use of subsampling, the extracted translation grammars are targeted for use with a specific test set. Our experiments were begun prior to the release of the blind newstest2010 shared task test set. Subsampling was performed using the development tuning set, news-test2008, and the development test set, newstest2009. Once the newstest2010 test set was released, the process of subsampling, alignment, and grammar extraction was repeated to obtain translation grammars targeted for use with the shared task test set.

>>>>

\author{Lane Schwartz\
\thanks{\ Research conducted as a visiting researcher at Johns Hopkins University}\
\\University of Minnesota\\Minneapolis, MN\\
{\tt lane@cs.umn.edu}% \And
%Chris Callison-Burch \\
%Johns Hopkins University \\
%Baltimore, MD\\
%{\tt ccb@cs.jhu.edu}
}

@@

\begin{abstract}
We present the Johns Hopkins University submission to the 2010 WMT shared translation task. We describe processing steps using open data and open source software used in our submission, and provide the scripts and configurations required to train, tune, and test our machine translation system.
\end{abstract}

@@

Research investigating natural language processing and computational linguistics can and should have an extremely low barrier to entry. The data with which we work is customarily available in common electronic formats. The computational techniques which we apply can typically be performed on commodity computing resources which are widely available. In short, there should be no reason why small research groups and even lone researchers should not be able to join and make substantive contributions furthering our field.
%
The reality is less encouraging.

@@

Freely available parallel corpora for numerous European languages have also been released in recent years. These include the Europarl \cite{Koehn-europarl} and JRC-Acquis \cite{Steinberger-2006} legislative corpora, each of which includes data for most EU language pairs. The smaller News Commentary corpora \cite{Callison-Burch2007a,Callison-Burch2008a} provide smaller amounts of parallel data in the news genre. The recent Fr-En $10^9$ \cite{WMT09-Findings} corpus aggregates huge numbers of parallel French-English sentences from the web.

@@

Figure \ref{dependencyGraph} shows a graph depicting the steps in our experimental workflow, and the dependencies between steps. Each node in the graph represents a step in the workflow; each step is implemented as a Make script that defines how to run the tools required in that step. In each experiment, an additional configuration script is provided for each experimental step, defining the parameters to be used when running that step in the current experiment. Optional front-end wrapper scripts can also be provided, allowing for a complete experiment to be run - from downloading data and software through truecasing translated results - by executing a single make file.

@@

Following \newcite{Joshua-WMT}, a subset of the available training sentences was selected via subsampling; training sentences are selected based on the estimated likelihood of each sentence being useful later for translating a particular test corpus.

@@

Because of the use of subsampling, the extracted translation grammars are targeted for use with a specific test set. Our experiments were begun prior to the release of the blind newstest2010 shared task test set. Subsampling was performed for the development tuning set, news-test2008, and the development test set, newstest2009. Once the newstest2010 test set was released, the process of subsampling, alignment, and grammar extraction was repeated to obtain translation grammars targeted for use with the shared task test set.
